Applied Measure Theory for Probabilistic Modeling

### 2022-05-18 paper/paper.tex
edits

We'll now discuss the mechanics of defining a measure, followed by 
\chad{add a description of the next subseciton here}

@@

Instead of \verb|logdensity_def|, users should typically call \verb|logdensity_rel(μ,ν,x)| (which computes $\frac{\dd μ}{\dd ν}(x)$), or \verb|logdensityof(μ,x)|, which gives the log-density relative to the root measure. \verb|logdensityof| was originally defined in \cite{DensityInterface.jl}.

>>>>

We'll now discuss the mechanics of defining a measure, followed by a description of the end-user perspective.

@@

Instead of \verb|logdensity_def|, users should typically call \verb|logdensity_rel(μ,ν,x)| (which computes $\frac{\dd μ}{\dd ν}(x)$), or \verb|logdensityof(μ,x)|, which gives the log-density relative to the root measure. \verb|logdensityof| was originally defined in \cite{DensityInterface.jl}, and provides a convenient common ground for those not accustomed to thinking of densities as being relative. We expect this to be especially useful for new users.
